PCoA with bray curtis on KO abundance

### 2019-10-21 scripts/10_genefamilies_KO_regroup.Rmd
update

>>>>

######################################## R ############################################

```{r}

# reorder the unstratified table
genef_KO <- read_tsv('../data/humann2_res/genefamily_split_KO/humann2_genefamilies_KO_regroup_relab_unstratified.tsv')%>% 
  rename(KO = names(.)[1]) %>% 
  rename_all(funs(str_replace(., '_Abundance-RPKs$','')))

pheno <- read_csv('../data/current_pheno.csv') %>% 
  filter(! Sampleid %in% c("1725E", "2222A" ,"2245A"))

genef_KO <- bind_cols(genef_KO[,1],genef_KO[,pheno$Sampleid]) 
all.equal(pheno$Sampleid, colnames(genef_KO)[2:ncol(genef_KO)])

```
```{r}
# look at the relab abundance of the pathways related to pantothenate for example
patha <- read_tsv('../data/humann2_res/humann2_final_out/humann2_pathabundance_relab_unstratified.tsv') %>% 
  # choose the pantothenate and fol
```

### 2019-10-21 scripts/13_PCoA_brayCurtis_KO_abundance.Rmd
update

@@

>>>>

## Looking at the whole table

@@

## Looking at subset of pathways

```{r}
vb_matrix <- pw %>% 
  filter(str_detect(pw, 'folate|pantothenate|cobalamin|biotin')) %>% 
  column_to_rownames('pw') %>% 
  as.matrix()

bc_dist <-  vegdist(t(vb_matrix), "bray")
pc_bc <- cmdscale(bc_dist, k = 2)
plot(pc_bc[,1], pc_bc[,2], col = pheno_col$tox_col, main = 'Pathway abundance color by tox')
plot(pc_bc[,1], pc_bc[,2], col = pheno_col$CR_col, main = 'Pathway abundance color by CR')

```
